% Please add the following required packages to your document preamble:
% \usepackage{longtable}
% Note: It may be necessary to compile the document several times to get a multi page table to line up properly

\begin{longtable}[c]{|l|l|p{4cm}|p{10cm}|}
\caption[Work Breakdown Structure]{Work Breakdown Structure necessary to complete objectives, incorporating required resources}
\label{tab:WBS}\\
\hline
\multicolumn{1}{|c|}{\textbf{WBS \#}} & \multicolumn{1}{c|}{\textbf{Name / Title}} & \multicolumn{1}{c|}{\textbf{Resources}} & \multicolumn{1}{c|}{\textbf{Description}} \\ \hline
\endfirsthead
\caption[]{Work Breakdown Structure necessary to complete objectives, incorporating required resources}
% \endhead
\label{tab:wbs}\\
\hline
WBS \#   & Name / Title & Resource & Description                           \\\hline
\endhead
%
1 & Project Initiation & \multirow{4}{*}{\parbox{4cm}{Team members,  Past literature, STELaRLab}} & \multirow{4}{*}{\parbox{10cm}{\scriptsize{Project initiating encompasses all early project admin and research. It includes early project scoping, finding a supervisor and sponsorship initiation.}}} \\ \cline{1-2}
1.1 & Team Formation &  &  \\ \cline{1-2}
1.2 & Preliminary Research &  &  \\ \cline{1-2}
1.3 & Sponsorship &  &  \\ \hline
2 & Project Charter & \multirow{13}{*}{\parbox{4cm}{Team members,  Past literature}} & \multirow{13}{*}{\parbox{10cm}{The project charter documents the commencement of the project. It outlines the intentions of and meta-information crucial to the project. It defines the aims and objectives of the project and acts as a check to ensure the project remains on track.}} \\ \cline{1-2}
2.1 & Abstract &  &  \\ \cline{1-2}
2.2 & Project Introduction - Background &  &  \\ \cline{1-2}
2.3 & Project Introduction - Literature Review &  &  \\ \cline{1-2}
2.4 & Project Introduction - Stakeholders &  &  \\ \cline{1-2}
2.5 & Objectives &  &  \\ \cline{1-2}
2.6 & Resources Required &  &  \\ \cline{1-2}
2.7 & WBS &  &  \\ \cline{1-2}
2.8 & Gantt Chart &  &  \\ \cline{1-2}
2.9 & Risk Assessment &  &  \\ \cline{1-2}
2.1 & Budget &  &  \\ \cline{1-2}
2.11 & Conclusion &  &  \\ \cline{1-2}
2.12 & Submission &  &  \\ \hline
3 & Physical Product & \multirow{18}{*}{\parbox[t][5cm]{4cm}{Team members, Past literature}} & \multirow{46}{*}{\parbox[t][15cm]{10cm}{This section covers the preliminary design, detailed design, manufacturing, assembly, and testing of the product. This section encompasses the main deliverables of the honours project.}} \\ \cline{1-2}
3.1 & Airframe &  &  \\ \cline{1-2}
3.1.1 & Design Initiation &  &  \\ \cline{1-2}
3.1.1.1 & Develop Constraints and Specifications &  &  \\ \cline{1-2}
3.1.1.2 & Prototyping &  &  \\ \cline{1-2}
3.1.2 & Preliminary Designs &  &  \\ \cline{1-2}
3.1.2.1 & Preliminary Sizing &  &  \\ \cline{1-2}
3.1.2.2 & Initial Layout \& Configurations &  &  \\ \cline{1-2}
3.1.2.3 & Evaluation and Iteration of Design &  &  \\ \cline{1-2}
3.1.2.4 & Preliminary Designs Review &  &  \\ \cline{1-2}
3.1.3 & Detailed Design &  &  \\ \cline{1-2}
3.1.3.1 & Initial Airfoil Selection &  &  \\ \cline{1-2}
3.1.3.2 & Initial Rotor Selection &  &  \\ \cline{1-2}
3.1.3.3 & External Airframe Design CAD &  &  \\ \cline{1-2}
3.1.3.4 & Internal Airframe Design CAD &  &  \\ \cline{1-2}
3.1.3.5 & Design Review &  &  \\ \cline{1-2}
3.1.3.6 & Engineering Drawings &  &  \\ \cline{1-2}
3.1.3.7 & Engineering Drawings Finalised &  &  \\ \cline{1-3}
3.1.4 & Manufacturiung & \multirow{7}{*}{\parbox{4cm}{Team members, Engineering Drawings}} &  \\ \cline{1-2}
3.1.4.1 & Airframe Prototype Manufacturing &  &  \\ \cline{1-2}
3.1.4.2 & Prototype Verification and Validation Buffer &  &  \\ \cline{1-2}
3.1.4.3 & Prototype Fully Manufactured &  &  \\ \cline{1-2}
3.1.4.4 & Final Airframe Manufacturing &  &  \\ \cline{1-2}
3.1.4.5 & Payload Manufacturing &  &  \\ \cline{1-2}
3.1.4.6 & Final System Complete &  &  \\ \cline{1-3} \newpage
3.1.5 & Testing & \multirow{6}{*}{\parbox{4cm}{Prototype system}} &  \\ \cline{1-2}
3.1.5.1 & Prototyping Test Design &  &  \\ \cline{1-2}
3.1.5.2 & Airframe Prototype Test &  &  \\ \cline{1-2}
3.1.5.3 & Design Review and Evaluation &  &  \\ \cline{1-2}
3.1.5.4 & Prototype Tests Complete &  &  \\ \cline{1-2}
3.1.5.5 & Prototype Test Analysis &  &  \\ \cline{1-3}
3.1.5.6 & Test Design & \multirow{6}{*}{\parbox{4cm}{Final System, URAF}} &  \\ \cline{1-2}
3.1.5.7 & Airframe Testing &  &  \\ \cline{1-2}
3.1.5.8 & Payload Preliminary Testing &  &  \\ \cline{1-2}
3.1.5.9 & Final Testing &  &  \\ \cline{1-2}
3.1.5.10 & Tests Complete &  &  \\ \cline{1-2}
3.1.5.11 & Analysis &  &  \\ \cline{1-3}
3.2 & Physical Architecture & \multirow{5}{*}{\parbox{4cm}{Team members, Past literature}} &  \\ \cline{1-2}
3.2.1 & Payload Design &  &  \\ \cline{1-2}
3.2.1.1 & Payload Preliminary Design &  &  \\ \cline{1-2}
3.2.1.2 & Detailed Payload Design &  &  \\ \cline{1-2}
3.2.1.3 & Payload Engineering Drawings &  &  \\ \cline{1-3}
3.2.2 & Power Systems & \multirow{4}{*}{\parbox{4cm}{Design Constraints, Team members}} &  \\ \cline{1-2}
3.2.2.1 & Motor Selection &  &  \\ \cline{1-2}
3.2.2.2 & Battery Selection &  &  \\ \cline{1-2}
3.2.2.3 & Controller Selection &  &  \\ \hline 
4 & Preliminary Report & \multirow{6}{*}{\parbox{4cm}{Team members, Past literature, Current Design work, Charter}} & \multirow{6}{*}{\parbox{10cm}{\scriptsize{The preliminary report acts as a complete description of the project at the time of its submission. It includes the specifications, objectives, summary of work completed, progress report, as well as project management.}}} \\ \cline{1-2}
4.1 & Preparatory Work &  &  \\ \cline{1-2}
4.2 & First Draft &  &  \\ \cline{1-2}
4.3 & First Draft Submission &  &  \\ \cline{1-2}
4.4 & Review &  &  \\ \cline{1-2}
4.5 & Preliminary Report Submission &  &  \\ \hline
5 & Abstract & \multirow{10}{*}{\parbox{4cm}{Team members, Current Design work, Charter, Preliminary Report}} & \multirow{10}{*}{\parbox{10cm}{This section includes a written abstract along with the video abstract. Both act as a advertisement for the project.}} \\ \cline{1-2}
5.1 & Structure &  &  \\ \cline{1-2}
5.2 & Refinement &  &  \\ \cline{1-2}
5.3 & Written Abstract First Draft &  &  \\ \cline{1-2}
5.4 & Review &  &  \\ \cline{1-2}
5.5 & Written Abstract Submission &  &  \\ \cline{1-2}
5.6 & Script &  &  \\ \cline{1-2}
5.7 & Filming &  &  \\ \cline{1-2}
5.8 & Editing &  &  \\ \cline{1-2}
5.9 & Video Abstract Submission &  &  \\ \hline  \newpage
6 & Seminar & \multirow{6}{*}{\parbox{4cm}{Team members, Current Design work, Charter, Preliminary Report, Abstracts}} & \multirow{6}{*}{\parbox{10cm}{The seminar presentation is a major deliverable for the overall success of the project. It acts as a showcase of the work done at the time of the presentation}} \\ \cline{1-2}
6.1 & Preparatory Work &  &  \\ \cline{1-2}
6.2 & Presentation Aid Creation &  &  \\ \cline{1-2}
6.3 & Presentation Rehearsal &  &  \\ \cline{1-2}
6.4 & Seminar Times &  &  \\ \cline{1-2}
6.5 & Presentation &  &  \\ \hline
7 & Ingenuity & \multirow{5}{*}{\parbox{4cm}{Team members, Current Design work, Charter, Preliminary Report, Abstracts,}} & \multirow{5}{*}{\parbox{10cm}{The Ingenuity expo is another major deliverable of the project. The assessment is based on the poster, a description, difficulty, work, and style and space.}} \\ \cline{1-2}
7.1 & Preparatory Work &  &  \\ \cline{1-2}
7.2 & Poster Design &  &  \\ \cline{1-2}
7.3 & Final Posters &  &  \\ \cline{1-2}
7.4 & Ingenuity &  &  \\ \hline
8 & Final Report & \multirow{6}{*}{\parbox{4cm}{Team members, Current Design work, Charter, Preliminary Report, Abstracts,}} & \multirow{6}{*}{\parbox{10cm}{This is the last major deliverable of the project. It is a complete record of the entire project, a technical document, as well as a project management strategy.}} \\ \cline{1-2}
8.1 & Preliminary Work &  &  \\ \cline{1-2}
8.2 & First Draft &  &  \\ \cline{1-2}
8.3 & First Draft Submission &  &  \\ \cline{1-2}
8.4 & Review &  &  \\ \cline{1-2}
8.5 & Final Submission &  &  \\ \hline
\end{longtable}
